The `ordertrans()` function

### 2021-08-13 inst/ordertrans.Rmd
named vector

>>>>

## Another use-case

How about this:

```{r}
(x <- c(d=2, a=3, c=4, b=3, e=6))
(y <- c(e=3, c=2, a=4, b=5, d=1))
x+y
```

Above, observe that R is behaving as intended $\ldots$ but is
potentially confusing.  Take the first element.  This has value
`2+5=7` and name `d` from the name of element 1 of `x`.  But it would
be reasonable to ask for the first element to be the sum of element
`d` of `x` and element `d` of `y`, which would be `2+1=3`.
This can be done with `ordertrans()`:

```{r}
ordertrans(x) + ordertrans(y)
```

See how `ordertrans()` has rearranged both `x` and `y` so that the
names are in alphabetical order.

But this is not perfect.  Consider:

```{r}
(z <- c(f=3, g=2, h=4, a=5, b=1))  # names NOT letters[1:5]
ordertrans(x) + ordertrans(z)  # arguably not well-defined
```

In this case the result is arguably incorrect.
